More straightforward movement variable definitions

### 2024-04-15 scripts/01.2_categorizeMovement.qmd
added age group; loaded targets

```{r setup}
#| include: false
library(tidyverse)
library(sf)
library(factoextra)
library(ade4)
load(here::here("data", "calcMovement", "movementBehavior.Rda"))
load(here::here("data", "dataPrep", "season_names.Rda"))
load(here::here("data", "derived", "cc.Rda"))

# retrieve age information, since it wasn't carried through in the movement analysis (oops)
load(here::here("data", "dataPrep", "downsampled_10min.Rda"))
ages <- map(downsampled_10min, ~.x %>%
              dplyr::select(Nili_id, seasonUnique, season, year, age, age_group) %>%
              distinct()) %>%
  purrr::list_rbind()
rm(downsampled_10min) # XXX need to do this in a faster way--attach age at an earlier stage probably

# Create a dataset with all seasons combined
allMovementBehavior <- purrr::list_rbind(movementBehavior)
movementBehaviorScaled <- allMovementBehavior %>%
  mutate(coreArea_log = log(coreArea),
         homeRange_log = log(homeRange)) %>%
  mutate(across(-c(Nili_id, seasonUnique, birth_year, sex), 
                function(x){as.numeric(as.vector(scale(x)))}))
```

>>>>

```{r setup}
#| include: false
library(tidyverse)
library(sf)
library(factoextra)
library(ade4)
library(here)
tar_config_set(store = here::here('_targets'))
tar_load(movementBehavior)
tar_load(season_names)
tar_load(cc)
tar_load(downsampled_10min)
# retrieve age information, since it wasn't carried through in the movement analysis (oops)
ages <- map(downsampled_10min, ~.x %>%
              dplyr::select(Nili_id, seasonUnique, season, year, age, age_group) %>%
              distinct()) %>%
  purrr::list_rbind()

# Create a dataset with all seasons combined
allMovementBehavior <- purrr::list_rbind(movementBehavior)
movementBehaviorScaled <- allMovementBehavior %>%
  mutate(coreArea_log = log(coreArea),
         homeRange_log = log(homeRange)) %>%
  mutate(across(-c(Nili_id, seasonUnique, birth_year, sex, age_group), 
                function(x){as.numeric(as.vector(scale(x)))}))
```
